INTELLIGENT SYSTEMS

### 2021-04-13 papers/paper_7.tex
the proposed method paper7

>>>>

\subsection{RELATED WORK}
\subsubsection{Mixed Noise Model}
The mixed noise is:
\begin{equation}
    n = \left\{ \\
    \begin{array}{cc}
        n_1, & with~probability~r_1,\\
        n_2, & with~probability~r_2,\\
        \cdots, & \cdots\\
        n_k, & with~probability~r_k,\\ 
    \end{array}
     \right\}
\end{equation}
where $ n_k $ is the \emph{k}-th noise component with probability density function (PDF) 
$ p_k $ and $ r_k $ are the unknown mixture ratios and thei sum is equal to 1.

\subsubsection{Weighted K-SVD Model}
The following work is based on the method proposed in \cite{0884882814}. After obtaining 
the value of the mixed-noise \emph{Probability Density Function} (PDF), and 
assuming that the noise has a uniform distribution, we can derive the \emph{negative 
log-likelihood} function (\ref{PDF}) useful as {\bfseries{fidelity term}} in the variational 
method. 
\begin{equation}\label{PDF}
    L(u,\Theta) = - \sum_{x\in\Omega}\ln\sum_{k=1}^Kr_kp_k(u(x)-f(x))
\end{equation}
In order for this probability to be extended to more types of noise 
distribution, it is necessary to perform an optimization that minimizes the 
upper limit of the function (\ref{H function}). 
\begin{eqnarray}\label{H function}
    H(u,\Theta,w) & = & - \sum_{x\in\Omega}\sum_{k=1}\ln\left[r_kp_k(u(x)-f(x))\right]w_k \nonumber \\
                  &   & + \sum_{x\in\Omega}\sum_{k=1}w_k(x)\ln{w_k(x)}  
\end{eqnarray}
To minimize H, a minimization of $ w $ must be performed, which is a probability 
indicates the noise at each pixel, and an iterative minimization of the other 
two variables $ u $ and $ \Theta $.

\subsubsection{IRCNN}
Another method \cite{0884882819} uses a CCN, based on the IRCNN model, to restore an 
image in which Gaussian noise is present. In this model, patches based $ L^2 $ 
residual loss functions are adopted. Unfortunately, if there are mixed-noises, 
this method does not produce satisfactory results.

\subsection{THE PROPOSED METHOD (EM-CNN)}
Removal of mixed-noise can be done with the following model:
\begin{equation}
    (u^*, \Theta^*, w^*) = \argmin_x\left\{H(u,\Theta,w) + \lambda_1S(u)\right\}
\end{equation}
where $ S $ as regularizer, such \emph{Total Variation Regularization} (TV) while $ \lambda_1 $ 
control the balance of the terms. By changing $u$ with an auxiliary function 
$v$, and applying the \emph{augmented Lagrangian method} (ALM) \cite{0884882833}, the minimizations 
on each component of $H$ ($u$, $\Theta$, $w$) change. The resolution of these 
minimizations allows to divide the mixed-noise removal problem into Gaussian 
noise removal (renewing $u$), choice of the fidelity term (renewing $v$), 
noise reduction (updating the Lagragian multiplier $u$), parameter estimation 
noise ($\Theta$ update) and error classification ($w$ update). The formula used by 
the model is able to handle different types of Gaussian noises such as impulse 
noise, mixed-noise Gaussian-impulse and many others. Each noise has 
a certain probability function pk, so just change this value in (\ref{H function}). A CNN 
can be used to learn Gaussian noise for different types of levels. In this paper 
the CNN based denoiser \cite{0884882819} was used. The weight $w$ is useful for assigning 
different fidelity terms to pixels contaminated by different levels of types of 
noise. The minimization of $\Theta$ and $w$ are part of EM processes. Thanks to 
these it is possible to extract information such as noise variations and the 
classification of this in different classes.
